---
title: "Five Words Analytics"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r}
urltodata<-"/home/webadmin/R/dtm-test/data/"
#arules
library(arules)
library(arulesViz)
library(gridExtra)
library(grid)
library(plotly)
dtm2<-read.table(paste0(urltodata,"dtm"), header=T,sep="")
dtm2<-as.matrix(dtm2)
wordtransactions<-as(dtm2,"transactions")
capture.output( rules <- apriori(wordtransactions, parameter = list(supp = 0.002, conf = 0.08)), file='NUL')
#rules <- apriori(wordtransactions, parameter = list(supp = 0.002, conf = 0.08))
#invisible(rules <- invisible(apriori(wordtransactions, parameter = list(supp = 0.002, conf = 0.08))));
options(digits=3)
rules.sorted<-sort(rules, by="confidence", decreasing=TRUE)
rulestoviz<-as(rules,"data.frame")
```
### These are the most common words that popped into your heads {data-width=100}

```{r}

library(wordcloud2)
wcsumv<-read.table(paste0(urltodata,"wc2sum"), header=T,sep="")
wordcloud2(wcsumv, size = 0.8,shape="circle")

```



### These are some numerical data about your answers

```{r}
itemFrequencyPlot(wordtransactions,topN=20,type="absolute")
mvec<-read.table(paste0(urltodata,"genderv"), header=T,sep="")
mvec<-c(mvec[1,],mvec[2,],mvec[3,])
names(mvec)=c("males","felmales","Xgender")
barplot(mvec)

```

### Here are some rules concerning your answers.

```{r}

grid.table(rulestoviz[1:10,])
plot(rules,method="graph",shading=NA,main="")
```

***

Legend: Support  - The fraction of which our item set occurs in our dataset;
  Confidence - probability that a rule is correct for a new transaction with items on the left;
  Lift - The ratio by which by the confidence of a rule exceeds the expected confidence 


### Graphic representation of rules
```{r}
plotly_arules(rules,method="matrix", measure = c("support", "confidence"),shading = "confidence", max = 1000)
```

### Graphic representation of rules
```{r}
plotly_arules(rules,method="two-key plot", measure = c("support", "confidence"),shading = "confidence", max = 1000)
```

### Graphic representation of rules
```{r}
plotly_arules(rules,method="scatterplot", measure = c("support", "confidence"),shading = "confidence", max = 1000)
```